Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 Experiments.tex
Notes clean-up

We tested % different
pilots % sizes, i.e. :
with 250, 500, 1000 and 2000 worker nodes and
%. For all of them, the walltime was
2 hours walltime. The time duration is determined by the Titan's walltime policy. Figure~\ref{fig:weakScal1a} depicts the average pilot
duration, the average execution time of AthenaMP, and the NGE pilot overhead as
function of the pilot size.

@@

% Firstly, w
We % can
observe that, despite some fluctuations due to external factors
% \footnote{such as the
(e.g., Titan's shared filesystem and the shared database used by the NGE), the
average execution time of AthenaMP % oscillates
ranges between 4200 and 4800 seconds. % Secondly, w
We % can
also observe that in all the cases the gap between AthenaMP execution times and
the pilot durations is minimal, although it slightly increases with the pilot
size. % By observing NGE's overhead, w
We % can
notice that NGE's overhead does grow linearly with the number of units.

@@

\mtnote{we dowe need to keep it below 2 hours?}\aanote{You are right. It was misleading. I Changed. Check if you like it.}

@@

We ran
% different
pilots
% sizes, i.e. :
with 256, 512, 1024 and 2048 worker nodes and
%. For all of them, the walltime was
3\mtnote{2?} hours walltime. Figure~\ref{fig:weakScal2a} depicts the average
pilot duration, the average execution time of five sequential
generations\mtnote{generations?}\aanote{Changed} of AthenaMP, and the corresponding overhead. We
% can
observe that the difference between the two durations is more marked than in the
previous experiments \mtnote{mostly due to the increased overhead?}\aanote{Well, I guess that's plain.}. Despite this, we notice that the growth of the overhead is consistent with the increment of the number of tasks per node for pilots with 256, 512 and 1024 worker nodes, and less than linear for the pilot with 2048 worker nodes.

@@

The last experiments % deals with
study strong scalability by running the same number of tasks for different pilot sizes. We used
2048 AthenaMP instances and % tested
pilots with 256, 512, 1024 and 2048 nodes. Thus, the number of AthenaMP generations is equal to eight times the size of the smallest pilot and corresponds to the size of the largest pilot. As a consequence, the number of consecutive generations of AthenaMP decreases with the pilot size by generating different dynamics within the pilots. These experiments are designed to investigate whether pilot overhead is affected by the degree of concurrency within the pilot and/or the number of tasks.  
\mtnote{Not sure I understand this sentence}\aanote{My fault. It should have been seven and null or 8 and 1. It depends on how we consider the word sequential. anyway, to avoid confusion I changed the sentence.}. Each AthenaMP instance
simulates sixteen events as in the previous experiment.

Figure \ref{fig:strongScala} % depicts
shows the average pilot duration and the average execution time of possibly
sequential AthenaMP instances.  We % can
notice that the difference between the pilot duration and the AthenaMP execution
times is almost constant for all the pilot sizes, although the overall duration
of the pilot decreases linearly with the pilot size.

>>>>

We tested  pilots  with 250, 500, 1000 and 2000 worker nodes and 2 hours
walltime. The time duration is determined by the Titan's walltime policy.
Figure~\ref{fig:weakScal1a} depicts the average pilot duration, the average
execution time of AthenaMP, and the NGE pilot overhead as function of the pilot
size.

@@

We observe that, despite some fluctuations due to external factors (e.g.,
Titan's shared filesystem and the shared database used by the NGE), the average
execution time of AthenaMP  ranges between 4200 and 4800 seconds.  We  also
observe that in all the cases the gap between AthenaMP execution times and the
pilot durations is minimal, although it slightly increases with the pilot size.
We  notice that NGE's overhead does grow linearly with the number of units.

@@

% \mtnote{we dowe need to keep it below 2 hours?}\aanote{You are right. It was misleading. I Changed. Check if you like it.}

@@

We ran pilots with 256, 512, 1024 and 2048 worker nodes and 3\mtnote{2?} hours
walltime. Figure~\ref{fig:weakScal2a} depicts the average pilot duration, the
average execution time of five sequential generations of AthenaMP, and the
corresponding overhead. We observe that the difference between the two durations
is more marked than in the previous experiments. Despite this, we notice that
the growth of the overhead is consistent with the increment of the number of
tasks per node for pilots with 256, 512 and 1024 worker nodes, and less than
linear for the pilot with 2048 worker nodes.

@@

The last experiments  study strong scalability by running the same number of
tasks for different pilot sizes. We used 2048 AthenaMP instances and  pilots
with 256, 512, 1024 and 2048 nodes. Thus, the number of AthenaMP generations is
equal to eight times the size of the smallest pilot and corresponds to the size
of the largest pilot. As a consequence, the number of consecutive generations of
AthenaMP decreases with the pilot size by generating different dynamics within
the pilots. These experiments are designed to investigate whether pilot overhead
is affected by the degree of concurrency within the pilot and/or the number of
tasks. Each AthenaMP instance simulates sixteen events as in the previous
experiment.

% \mtnote{Not sure I understand this sentence}\aanote{My fault. It should
% have been seven and null or 8 and 1. It depends on how we consider the word
% sequential. anyway, to avoid confusion I changed the sentence.}.

Figure \ref{fig:strongScala}  shows the average pilot duration and the average
execution time of possibly sequential AthenaMP instances.  We  notice that the
difference between the pilot duration and the AthenaMP execution times is almost
constant for all the pilot sizes, although the overall duration of the pilot
decreases linearly with the pilot size.
